---
title: "BEIPIR"
author: "Dr. Jiayang Sun, Gabriel Brehm"
date: "2023-02-22"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(ggplot2)
library(plotly)
library(readxl)
library(rdist)
library(forcats)
library(car)
library(ggthemes)
```

```{r read_in, include=FALSE}

baseline <- read_excel("OG Files/BEIPIR Master Key_Jan 2023v3b.xlsx", 
    sheet = "Baseline visit only")

all_at_once <- read_excel("OG Files/BEIPIR Master Key_Jan 2023v3b.xlsx", 
    sheet = "Everything all together")

```

```{r data_setup_and_wrangling, include=FALSE}
# All At Once Data
all_at_once <- all_at_once %>% mutate(across(SUBJ:YRIN, as.numeric))
all_at_once <- all_at_once %>% mutate(across(RACE:PRI, as_factor))
all_at_once <- all_at_once %>% mutate(across(IMAT, as.numeric))
all_at_once <- all_at_once %>% mutate(across(WCTP:SMOK, as_factor))
all_at_once <- all_at_once %>% mutate(across(SYRS:HGA1, as.numeric))
all_at_once <- all_at_once %>% mutate(across(LIVS:PRFQ, as_factor))
all_at_once <- all_at_once %>% mutate(across(HRSC, as.numeric))
all_at_once <- all_at_once %>% mutate(across(EMPL:EDUC, as_factor))

# Baseline data (obv I figured out the tidyverse way to do this later lol)
baseline$SUBJ <- as.integer(baseline$SUBJ)
baseline$VINO <- as.integer(baseline$VINO)
baseline$YRIN <- as.numeric(baseline$YRIN)
baseline$RACE <- as_factor(baseline$RACE)
baseline$ETHN <- as_factor(baseline$ETHN)
baseline$GEND <- as_factor(baseline$GEND)
baseline$LOI <- as_factor(baseline$LOI)
baseline$ASIA <- as_factor(baseline$ASIA)
baseline$PRI <- as_factor(baseline$PRI)
baseline$IMAT <- as.numeric(baseline$IMAT)
baseline$NUTI <- as_factor(baseline$NUTI)
baseline$BOI <- as_factor(baseline$BOI)
baseline$BLI <- as_factor(baseline$BLI)
baseline$VASC <- as_factor(baseline$VASC)
baseline$RESP <- as_factor(baseline$RESP)
baseline$PNEU <- as_factor(baseline$PNEU)
baseline$DIAB <- as_factor(baseline$DIAB)
baseline$DEPR <- as_factor(baseline$DEPR)
baseline$ANXI <- as_factor(baseline$ANXI)
baseline$PAIN <- as_factor(baseline$PAIN)
baseline$SLEP <- as_factor(baseline$SLEP)
baseline$ALCO <- as_factor(baseline$ALCO)
baseline$NODR <- as_factor(baseline$NODR)
baseline$DRUG <- as_factor(baseline$DRUG)
baseline$SMOK <- as_factor(baseline$SMOK) 
baseline$SYRS <- as.numeric(baseline$SYRS) # smoking years is interesting because there are numbers (for number of smmoking years), N/A (for non-smokers), and "unk" for unknown (data not collected). might want to split this into 2 later: one as factor and one as actual years
baseline$BMI <- as.numeric(baseline$BMI)
baseline$LIVS <- as_factor(baseline$LIVS)
baseline$EMPL <- as_factor(baseline$EMPL)
baseline$MARS <- as_factor(baseline$MARS)
baseline$EDUC <- as_factor(baseline$EDUC)



```

# Visualizations

```{r themes, include=FALSE}
g.theme <- theme_stata()

```

NOTE: 1 ALBUMIN VALUE IS AT 999, NEED TO UNDERSTAND THAT

```{r baseline_visualizations, fig.width=10, echo=FALSE, warning=FALSE, }
# Pick only visit 1
visit_one <- all_at_once[, -46:-56] %>% 
  dplyr::filter(VINO == 1) %>%
  dplyr::select(-SUBJ, -VINO) %>%
  dplyr::filter(ALBM < 999)

# NOTE: 1 ALBUMIN VALUE IS AT 999, NEED TO UNDERSTAND THAT

categoricals <- visit_one %>% dplyr::select(is.factor | IMAT)
numericals <- visit_one %>% dplyr::select(is.numeric)

# Make categorical violins against IMAT
for (i in colnames(categoricals)) {
  if(i != "IMAT") {
    p <- visit_one %>% ggplot(aes_string(x = i, y = "IMAT")) +
    geom_violin() +
    labs(x = i) +
    g.theme
  
    print(p)
  }
}

# Make counts for categorical vs. PRI
for (i in colnames(categoricals)) {
  if(i != "PRI") {
    p <- visit_one %>% ggplot(aes_string(x = i, y = "PRI")) +
      geom_count() +
      labs(x = i) +
      g.theme
    
    print(p)
  }
}

# Make violins for PRI against numericals
for (i in colnames(numericals)) {
  p <- visit_one %>% ggplot(aes_string(x = "PRI", y = i)) +
  geom_violin() +
  labs(y = i) +
  g.theme

  print(p)
}

# Make histograms for numerical data
for (i in colnames(numericals)) {
  p <- visit_one %>% ggplot(aes_string(x = i)) +
    geom_histogram(bins = 30) +
    labs(x = i) +
    g.theme
  
  print(p)
}


# Make LOG histograms for numerical data
# for (i in colnames(numericals)) {
#   p <- visit_one %>% ggplot(aes_string(x = log(i))) +
#     geom_histogram(bins = 30) +
#     labs(x = i) +
#     g.theme
#   
#   print(p)
#   
# }

# Make scatters for numerical data against IMAT

for (i in colnames(numericals)) {
  if(i != "IMAT") {
    p <- visit_one %>% ggplot(aes_string(x = i, y = "IMAT")) +
      geom_point() +
      labs(x = i) +
      g.theme
    
    print(p)
  }
}

pairs(numericals)

```


# Numerical EDA

Try looking at distances between points (if possible), correlations, partial correlations

```{r baseline_numerical_EDA, echo=FALSE}
print("Summary")
summary(visit_one)

print("Partial Correlations")
Sigma <- cor(na.omit(numericals))
Sigma.inv <- solve(Sigma)
Omega <- -cov2cor(Sigma.inv)
diag(Omega) <- 1
Omega

print("Standardized Distances Check")
scaled_numericals <- scale(numericals)
numericals.scaled_dist <- pdist(scaled_numericals, "euclidean")
boxplot(as.vector(numericals.scaled_dist))
```
A slight tail indicates some potential signal in the noise, though it's not completely clear that there is very much signal here.

## Some First Models

### Just IMAT

```{r first_linear_reg, echo=FALSE}
# Just some stuff that looked good in the EDA
print("Guesses from EDA")
linear.a <- lm(log(IMAT) ~ log(YRIN) + log(AGEN) + log(HGA1) + ETHN + LOI + ASIA + PRI + BED + PRAH, data = visit_one)
summary(linear.a)

print("Refining a bit")
# Taking out BED
linear.b <- lm(log(IMAT) ~ log(YRIN) + log(AGEN) + ETHN + LOI + ASIA + PRI, data = visit_one)
summary(linear.b)

```

### Just PRI

```{r first_logistic, echo=FALSE}
#omitting PRFQ because too many NAs
logit_data <- visit_one %>% dplyr::filter(PRI == 'Y' | PRI == 'N')

logit.a <- glm(PRI ~ log(IMAT) + log(YRIN) + log(AGEN) + log(HGA1) + LOI + ASIA + BED + MATT + WCTP + CUTP + SHC, data = logit_data, family = binomial)
summary(logit.a)

#Improvement? IDK what i'm doing here lol
logit.b <- glm(PRI ~ log(IMAT) + log(YRIN) + log(AGEN) + LOI + ASIA + WCTP + CUTP + SHC, data = logit_data, family = binomial)
summary(logit.b)

```
### Multivariate Model
PRI & log(IMAT) vs. potential explainers, just seeing how this looks

```{r first_multivariate, echo=FALSE}
multivariate_model <- lm(cbind(PRI, log(IMAT)) ~ log(YRIN) + log(AGEN) + log(HGA1) + LOI + ASIA + BED + MATT + WCTP + CUTP + SHC + PRFQ, data = visit_one)

summary(multivariate_model)
vcov(multivariate_model)

#Anova(multivariate_model)

```
