---
title: "BEIPIR"
author: "Dr. Jiayang Sun, Gabriel Brehm"
date: "2023-02-22"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(ggplot2)
library(readxl)
library(rdist)
library(forcats)
library(car)
library(ggthemes)
library(FactoMineR)
library(factoextra)
library(rpart)
library(rpart.plot)
library(rattle)
library(e1071)
library(ranger)
library(caret)
library(ggparty)
library(ggforce)
```

```{r read_in, include=FALSE}

baseline <- read_excel("OG Files/BEIPIR Master Key_Jan 2023v3b.xlsx", 
    sheet = "Baseline visit only")

all_at_once <- read_excel("OG Files/BEIPIR Master Key_Jan 2023v3b.xlsx", 
    sheet = "Everything all together")

```

```{r data_setup_and_wrangling, include=FALSE}
# All At Once Data
all_at_once <- all_at_once %>% mutate(across(SUBJ:YRIN, as.numeric))
all_at_once <- all_at_once %>% mutate(across(RACE:PRI, factor))
all_at_once <- all_at_once %>% mutate(across(IMAT, as.numeric))
all_at_once <- all_at_once %>% mutate(across(WCTP:SMOK, factor))
all_at_once <- all_at_once %>% mutate(across(SYRS:HGA1, as.numeric))
all_at_once <- all_at_once %>% mutate(across(LIVS:PRFQ, factor))
all_at_once <- all_at_once %>% mutate(across(HRSC, as.numeric))
all_at_once <- all_at_once %>% mutate(across(EMPL:EDUC, factor))

# Baseline data (obv I figured out the tidyverse way to do this later lol)
baseline$SUBJ <- as.integer(baseline$SUBJ)
baseline$VINO <- as.integer(baseline$VINO)
baseline$YRIN <- as.numeric(baseline$YRIN)
baseline$RACE <- as_factor(baseline$RACE)
baseline$ETHN <- as_factor(baseline$ETHN)
baseline$GEND <- as_factor(baseline$GEND)
baseline$LOI <- as_factor(baseline$LOI)
baseline$ASIA <- as_factor(baseline$ASIA)
baseline$PRI <- as_factor(baseline$PRI)
baseline$IMAT <- as.numeric(baseline$IMAT)
baseline$NUTI <- as_factor(baseline$NUTI)
baseline$BOI <- as_factor(baseline$BOI)
baseline$BLI <- as_factor(baseline$BLI)
baseline$VASC <- as_factor(baseline$VASC)
baseline$RESP <- as_factor(baseline$RESP)
baseline$PNEU <- as_factor(baseline$PNEU)
baseline$DIAB <- as_factor(baseline$DIAB)
baseline$DEPR <- as_factor(baseline$DEPR)
baseline$ANXI <- as_factor(baseline$ANXI)
baseline$PAIN <- as_factor(baseline$PAIN)
baseline$SLEP <- as_factor(baseline$SLEP)
baseline$ALCO <- as_factor(baseline$ALCO)
baseline$NODR <- as_factor(baseline$NODR)
baseline$DRUG <- as_factor(baseline$DRUG)
baseline$SMOK <- as_factor(baseline$SMOK) 
baseline$SYRS <- as.numeric(baseline$SYRS) # smoking years is interesting because there are numbers (for number of smmoking years), N/A (for non-smokers), and "unk" for unknown (data not collected). might want to split this into 2 later: one as factor and one as actual years
baseline$BMI <- as.numeric(baseline$BMI)
baseline$LIVS <- as_factor(baseline$LIVS)
baseline$EMPL <- as_factor(baseline$EMPL)
baseline$MARS <- as_factor(baseline$MARS)
baseline$EDUC <- as_factor(baseline$EDUC)

# Fix Entry Errors
levels(all_at_once$ETHN) <- c("Hs/L", "Hs/L", "Not Hs/L", "unk")
levels(all_at_once$WCTP) <- c("AmnWC", "MWc", "MWc", "OWc", "PWc", "TRWc")
levels(all_at_once$CUTP) <- c("ACu", "ACu", "FCu", "FCu", "LCu", "NoCu", "OCu")

# Albumin values of 999 are equivalent to NA


# Pick only visit 1
visit_one <- all_at_once[, -46:-56] %>% 
  dplyr::filter(VINO == 1) %>%
  dplyr::select(-SUBJ, -VINO) %>%
  dplyr::filter(ALBM < 999)



# Bin the continuous variables based on the following criteria:
# AGEN: 
# 0 - 40: young
# 41 - 55: middle age
# 56-65: old mid
# 66+: old
# 
# YRIN:
# 0-8: low
# 9-23: mid
# 24+: high
# 
# IMAT:
# 0-15
# 16-21
# 21-50
# 50+
# 
# SYRS:
# 5
# 6-10
# 11-20
# 21+
# 
# HT, WT - ignore
# 
# BMI: 
# 22
# 25
# 30
# 40?
# 
# ALBM
# 0-3: low
# 3-5.5: NORMAL
# 5.5+ high
# 
# HGA1:
# 0-5.7: normal
# 5.7+: pre-diabetic
# 6.0+: diabetic
# 
# HRSC:
# 0-4:
# 5-12:
# 13+:

vone_binned <- visit_one %>% mutate(AGEN = cut(AGEN, breaks = c(-Inf, 40, 55, 65, Inf), labels = c("yng", "mid", "old", "sen")),
                                    YRIN = cut(YRIN, breaks = c(-Inf, 8, 23, Inf), labels = c("sht", "med", "lng")),
                                    IMAT = cut(IMAT, breaks = c(-Inf, 15, 21, 50, Inf), labels = c("low", "med", "hi", "xhi")),
                                    SYRS = cut(SYRS, breaks = c(-Inf, 5, 10, 20, Inf), labels = c("low", "med", "hi", "xhi")),
                                    BMI = cut(BMI, breaks = c(-Inf, 22, 25, 30, Inf), labels = c("low", "med", "hi", "xhi")),
                                    ALBM = cut(ALBM, breaks = c(-Inf, 3, 5.5, Inf), labels = c("low", "nrm", "hi")),
                                    HGA1 = cut(HGA1, breaks = c(-Inf, 5.7, 6.0, Inf), labels = c("nrm", "pred", "diab")),
                                    HRSC = cut(HRSC, breaks = c(-Inf, 4, 12, Inf), labels = c("low", "med", "hi"))) %>%
  select(-WT, -HT)

categoricals <- visit_one %>% dplyr::select(where(is.factor) | IMAT)
continuous <- visit_one %>% dplyr::select(where(is.numeric))

```

# Visualizations

```{r themes, include=FALSE}
g.theme <- theme_stata()
```


```{r baseline_visualizations, fig.width=10, echo=FALSE, warning=FALSE, eval=FALSE}



# Make categorical violins against IMAT
for (i in colnames(categoricals)) {
  if(i != "IMAT") {
    p <- visit_one %>% ggplot(aes_string(x = i, y = "IMAT")) +
    geom_violin() +
    labs(x = i) +
    g.theme
  
    print(p)
  }
}

# Make counts for categorical vs. PRI
for (i in colnames(categoricals)) {
  if(i != "PRI") {
    p <- visit_one %>% ggplot(aes_string(x = i, y = "PRI")) +
      geom_count() +
      labs(x = i) +
      g.theme
    
    print(p)
  }
}

# Make violins for PRI against continuous
for (i in colnames(continuous)) {
  p <- visit_one %>% ggplot(aes_string(x = "PRI", y = i)) +
  geom_violin() +
  labs(y = i) +
  g.theme

  print(p)
}

# Make histograms for numerical data
for (i in colnames(continuous)) {
  p <- visit_one %>% ggplot(aes_string(x = i)) +
    geom_histogram(bins = 30) +
    labs(x = i) +
    g.theme
  
  print(p)
}


# Make LOG histograms for numerical data
# for (i in colnames(continuous)) {
#   p <- visit_one %>% ggplot(aes_string(x = log(i))) +
#     geom_histogram(bins = 30) +
#     labs(x = i) +
#     g.theme
#   
#   print(p)
#   
# }

# Make scatters for numerical data against IMAT

for (i in colnames(continuous)) {
  if(i != "IMAT") {
    p <- visit_one %>% ggplot(aes_string(x = i, y = "IMAT")) +
      geom_point() +
      labs(x = i) +
      g.theme
    
    print(p)
  }
}

pairs(continuous)

```

```{r baseline_categorical_EDA_reduced, warning=FALSE, echo=FALSE}


categoricals <- visit_one %>% dplyr::select(is.factor | IMAT)
continuous <- visit_one %>% dplyr::select(is.numeric)

p <- visit_one %>% ggplot(aes(x = PRI)) +
  geom_violin(aes(y = IMAT)) +
  geom_text(stat='count', aes(label=..count..)) +
  g.theme
print(p)

p <- visit_one %>% ggplot(aes(x = LOI)) +
  geom_violin(aes(y = IMAT)) +
  geom_text(stat='count', aes(label=..count..)) +
  g.theme
print(p)


p <- visit_one %>% ggplot(aes(x = ASIA)) +
  geom_violin(aes(y = IMAT)) +
  geom_text(stat='count', aes(label=..count..)) +
  g.theme
print(p)


p <- visit_one %>% ggplot(aes(x = GEND)) +
  geom_violin(aes(y = IMAT)) +
  geom_text(stat='count', aes(label=..count..)) +
  g.theme
print(p)


p <- visit_one %>% ggplot(aes(x = BOI)) +
  geom_violin(aes(y = IMAT)) +
  geom_text(stat='count', aes(label=..count..)) +
  g.theme
print(p)


p <- visit_one %>% ggplot(aes(x = BLI)) +
  geom_violin(aes(y = IMAT)) +
  geom_text(stat='count', aes(label=..count..)) +
  g.theme
print(p)


# Make violins for PRI against continuous
for (i in colnames(continuous)) {
  p <- visit_one %>% ggplot(aes_string(x = "PRI")) +
  geom_violin(aes_string(y = i)) +
  geom_text(stat='count', aes(label=..count..)) +
  labs(y = i) +
  g.theme

  print(p)
}

# Make counts for categorical vs. PRI

p <- visit_one %>% ggplot(aes(x = LOI, y = PRI)) +
  geom_count() +
  g.theme
print(p)
table(categoricals$LOI, categoricals$PRI)

p <- visit_one %>% ggplot(aes(x = ASIA, y = PRI)) +
  geom_count() +
  g.theme
print(p)
table(categoricals$ASIA, categoricals$PRI)

p <- visit_one %>% ggplot(aes(x = CUTP, y = PRI)) +
  geom_count() +
  g.theme
print(p)
table(categoricals$CUTP, categoricals$PRI)

p <- visit_one %>% ggplot(aes(x = BED, y = PRI)) +
  geom_count() +
  g.theme
print(p)
table(categoricals$BED, categoricals$PRI)


# Make scatters for numerical data against IMAT


continuous %>% dplyr::select(-HGA1, -ALBM, -WT, -HT, -HRSC) %>% pairs(panel = panel.smooth, lwd = 2, cex = 1.5, col = 4)

```


# Continuous EDA

Try looking at distances between points (if possible), correlations, partial correlations

```{r baseline_numerical_EDA, echo=FALSE}
print("Summary")
summary(visit_one)

print("Partial Correlations")
Sigma <- cor(na.omit(continuous))
Sigma.inv <- solve(Sigma)
Omega <- -cov2cor(Sigma.inv)
diag(Omega) <- 1
Omega

corrplot::corrplot(Omega)

## Standardized distances 
print("Standardized Distances Check")
scaled_continuous <- scale(continuous)
continuous.scaled_dist <- pdist(na.omit(scaled_continuous), "euclidean")/sqrt(ncol(continuous)-1)
boxplot(as.vector(continuous.scaled_dist))
```
A slight tail indicates some potential signal in the noise, though it's not completely clear that there is very much signal here. This could also just indicate that the signal is more present in the categorical than the continuous variables.

```{r correspondence, fig.width=10, fig.height=8}
# Try binning continuous variables using CART.
# Use 'cex' to pick size of things, use ggplot for plotting of analysis
# Try plotting first 3 dimensions
# Set a diff color for each variable 
# After plotting and understanding, remove variables that don't seem to have a relationship so that plot looks cleaner
# use lower case
# take out center variables
# draw densities around remaining variables

mca_dat <- vone_binned

cats = apply(mca_dat, 2, function(x) nlevels(as.factor(x)))

visit_one.ca <- MCA(X = mca_dat, graph = FALSE)
mca_eig <- as.data.frame(visit_one.ca$eig)
# data frames for ggplot

# mca1_vars_df = data.frame(visit_one.ca$var$coord, Variable = rep(names(cats), 
#     cats))
# mca1_obs_df = data.frame(visit_one.ca$ind$coord)

scree <- mca_eig %>% ggplot(aes(x = 1:nrow(mca_eig), y = `percentage of variance`)) +
  geom_point() +
  geom_line() +
  g.theme
scree
# 
# 
# # plot of variable categories
# mca.plot <- ggplot(data = mca1_vars_df, aes(x = Dim.1, y = Dim.2, label = rownames(mca1_vars_df))) +
#   geom_hline(yintercept = 0, colour = "gray70") +
#   geom_vline(xintercept = 0, colour = "gray70") +
#   # geom_point(colour = "gray50", alpha = 0.7) +
#   geom_density2d(colour = "gray80") +
#   geom_text(data = mca1_vars_df, aes(x = Dim.1, y = Dim.2, label = rownames(mca1_vars_df), colour = Variable), size = 2.5) +
#   ggtitle("MCA plot of variables using R package FactoMineR") + scale_colour_discrete(name = "Variable") +
#   g.theme
# mca.plot

# options(repr.plot.width =20, repr.plot.height =20)

# ggsave("mca_plot.png", plot = mca.plot, width = 30, height = 30)

var_names <- rownames(visit_one.ca$var$contrib)
undesired_vars1 <- c("YRIN.NA", "ASIA_Unk", "PRI_Unk", "IMAT.NA", "DIAB_unk", "PAIN_N/A", "PAIN_unk", "SLEP_N/A", "SLEP_unk", "HGA1.NA", "SHC_unk", "USHC_unk", "PRAH_unk", "PRFQ_unk", "HRSC.NA", "MARS_unk")

desired_variables <- var_names[!var_names %in% undesired_vars1] 


p <- fviz_mca_var(visit_one.ca, col.var = "steelblue", repel = TRUE, 
             select.var = list(name = desired_variables)) +
  geom_circle(aes(x0 = -1.1, y0 = 0.9, r = 0.4), color = "red", fill = "transparent") +
  geom_circle(aes(x0 = 1.25, y0 = 0.75, r = 0.2), color = "red", fill = "transparent") +
  geom_circle(aes(x0 = 1.6, y0 = -1.25, r = 0.4), color = "red", fill = "transparent") +
  geom_ellipse(aes(x0 = 0, y0 = -0.97, a = 0.53, b = 0.3, angle = 0), color = "red", fill = "transparent") +
  g.theme
p
ggsave("correspondence.png", p, dpi = 300)
```


## Some First Models

### Just IMAT

```{r first_linear_reg, echo=FALSE}
# Just some stuff that looked good in the EDA
#ln(y/(1-y))
print("Guesses from EDA")
linear.a <- lm(log(IMAT/(100-IMAT)) ~ YRIN + AGEN + HGA1 + LOI + ASIA + PRI + BED + PRAH, data = visit_one)
summary(linear.a)


print("Transformed Guesses from EDA")
linear.b <- lm(log(IMAT/(100-IMAT)) ~ log(YRIN) + log(AGEN) + log(HGA1) + LOI + ASIA + PRI + BED + PRAH, data = visit_one)
summary(linear.b)


print("Refining a bit")
# Taking out BED
linear.c <- lm(log(IMAT/(100-IMAT)) ~ log(YRIN) + log(AGEN) + LOI + ASIA + PRI, data = visit_one)
summary(linear.c)

```

### Just PRI

```{r class_data}
# Set up data to make sure that all points have a response classification
# clinical, biological, and social factors should take precedence over other factors like equipment which likely just show attempts to treat the issues at hand

class_data <- visit_one %>% dplyr::filter(PRI == 'Y' | PRI == 'N')
class_binned <- vone_binned %>% dplyr::filter(PRI == 'Y' | PRI == 'N') %>%
  select(-WCTP, -CUTP, -BED, -MATT, -SHC, -USHC, -PRAH, -PRFQ)

levels(class_data$PRI) <- c("N", "N", "Y")
levels(class_binned$PRI) <- c("N", "N", "Y")

# Randomly split to ~80% training, ~20% test
train_samp <- sample(nrow(class_data), size = round(0.8*nrow(class_data)), replace = FALSE)

class.train <- class_data[train_samp,]
class.test <- class_data[-train_samp,]
binned.train <- class_binned[train_samp,]
binned.test <- class_binned[-train_samp,]

```

```{r first_logistic, echo=FALSE}
#omitting PRFQ because too many NAs

logistic.a <- glm(PRI ~ log(IMAT) + log(YRIN) + log(AGEN) + log(HGA1) + LOI + ASIA + BED + MATT + WCTP + CUTP + SHC, data = class.train, family = binomial)
summary(logistic.a)

#Improvement? IDK what i'm doing here lol
logistic.b <- glm(PRI ~ log(IMAT) + log(YRIN) + log(AGEN) + LOI + ASIA + WCTP + CUTP + SHC, data = class.train, family = binomial)
summary(logistic.b)

```


```{r tree_class, fig.width=10, fig.height=7}
# Use LOOCV (leave-one-out-cross-validation)
# make complexity parameter smaller (cp), maybe 0.001, and try again, then prune
# www.statmethods.net/advstats/cart.html
# Try a random forest as well
# Check dr. Sun's webpage for other tree plot methods
# force tree to include sleep, pain, imat, age, ASIA
# try using stumps for each variable to figure out how predictive they are individually
# pri.cart_all_data <- rpart(PRI ~ ., data = class_data, method = "class", control = rpart.control(xval = nrow(class_data)))

pri.no_test <- rpart(PRI ~ ., data = class_data, method = "class", control = rpart.control(xval = nrow(class_data)))
pri.cart <- rpart(PRI ~ ., data = class.train, method = "class", control = rpart.control(xval = nrow(class.train)))
pri.cart.binned <- rpart(PRI ~ ., data = binned.train, method = "class", control = rpart.control(xval = nrow(binned.train)))
pri.cart.forced <- rpart(PRI ~ SLEP + PAIN + IMAT + AGEN + YRIN + ASIA, data = class.train, method = "class", control = rpart.control(xval = nrow(class.train)))
pri.cart.forced.binned <- rpart(PRI ~ SLEP + PAIN + IMAT + AGEN + YRIN + ASIA, data = binned.train, method = "class", control = rpart.control(xval = nrow(binned.train)))

tree_plot <- function(tree, title) {
  g <- ggparty(as.party(tree)) + 
  ggtitle(title) +
  geom_edge() +
  geom_edge_label() +
  geom_node_label(line_list = list(aes(label = splitvar),
                                   aes(label = paste0("N=", nodesize), 
                                       size = 10)),
                  line_gpar = list(list(size = 13), 
                                   list(size = 10)), 
                  ids = "inner") +
  geom_node_plot(gglist = list(
    geom_bar(aes(x = "", fill = PRI),
             position = position_fill(), color = "black"),
      theme_minimal(),
      scale_fill_manual(values = c("gray50", "gray80"), guide = FALSE),
      scale_y_continuous(breaks = c(0, 1)),
    xlab(""), 
    ylab("Probability"),
    geom_text(aes(x = "", group = PRI,
                  label = stat(count)),
              stat = "count", position = position_fill(), vjust = 1.1)),
    shared_axis_labels = TRUE)
  return(g)
}

confusion_matrix <- function(object, newdata) {
  preds <- as.data.frame(predict(object, newdata)) %>% mutate(YorN = case_when(
  Y >= 0.5 ~ "Y",
  TRUE ~ "N"
)) %>% mutate(across(YorN, as.factor))
  
  caret::confusionMatrix(data = preds$YorN, reference = newdata$PRI, positive = "Y")
}

p.full <- tree_plot(pri.cart, 
          title = "PRI Classification Tree (Full)") +
  theme(panel.background = element_rect(fill = "white"))

p.no_test <- tree_plot(pri.no_test, 
          title = "PRI Classification Tree (Full) With All Data") +
  theme(panel.background = element_rect(fill = "white"))

p.binned <- tree_plot(pri.cart.binned,
          title = "Binned PRI Classification Tree") +
  theme(panel.background = element_rect(fill = "white"))

p.restrict <- tree_plot(pri.cart.forced,
          title = "Reduced Variables PRI Classification Tree") +
  theme(panel.background = element_rect(fill = "white"))

p.restrict.binned <- tree_plot(pri.cart.forced.binned,
                               title = "Reduced Variables with Binning PRI Classification Tree") +
  theme(panel.background = element_rect(fill = "white"))

                               

c.full.test <- confusion_matrix(pri.cart, class.test)
c.full.train <- confusion_matrix(pri.cart, class.train)
c.binned.test <- confusion_matrix(pri.cart.binned, binned.test)
c.binned.train <- confusion_matrix(pri.cart.binned, binned.train)
c.forced.test <- confusion_matrix(pri.cart.forced, class.test)
c.forced.train <- confusion_matrix(pri.cart.forced, class.train)
c.forced.binned.test <- confusion_matrix(pri.cart.forced.binned, binned.test)
c.forced.binned.train <- confusion_matrix(pri.cart.forced.binned, binned.train)

trees <- data.frame(matrix(nrow = 8, ncol = 5))
colnames(trees) <- c("Tree", "Accuracy", "Sensitivity", "Specificity", "Precision")

trees[1,] <- c("Full/test", c.full.test$overall[1], c.full.test$byClass[1], c.full.test$byClass[2], c.full.test$byClass[5])
trees[2,] <- c("Full/train", c.full.train$overall[1], c.full.train$byClass[1], c.full.train$byClass[2], c.full.train$byClass[5])
trees[3,] <- c("Binned/test", c.binned.test$overall[1], c.binned.test$byClass[1], c.binned.test$byClass[2], c.binned.test$byClass[5])
trees[4,] <- c("Binned/train", c.binned.train$overall[1], c.binned.train$byClass[1], c.binned.train$byClass[2], c.binned.train$byClass[5])
trees[5,] <- c("Restricted/test", c.forced.test$overall[1], c.forced.test$byClass[1], c.forced.test$byClass[2], c.forced.test$byClass[5])
trees[6,] <- c("Restricted/train", c.forced.train$overall[1], c.forced.train$byClass[1], c.forced.train$byClass[2], c.forced.train$byClass[5])
trees[7,] <- c("Restricted & Binned/test", c.forced.binned.test$overall[1], c.forced.binned.test$byClass[1], c.forced.binned.test$byClass[2], c.forced.binned.test$byClass[5])
trees[8,] <- c("Restricted & Binned/train", c.forced.binned.train$overall[1], c.forced.binned.train$byClass[1], c.forced.binned.train$byClass[2], c.forced.binned.train$byClass[5])

trees %>% mutate(across(Accuracy:Precision, as.numeric)) 

trees <- rapply(object = trees, f = round, classes = "numeric", how = "replace", digits = 3) 


```



```{r tree_stumps}

tree_plot <- function(tree, title) {
  g <- ggparty(as.party(tree)) + 
  ggtitle(title) +
  geom_edge() +
  geom_edge_label() +
  geom_node_label(line_list = list(aes(label = splitvar),
                                   aes(label = paste0("N=", nodesize), 
                                       size = 10)),
                  line_gpar = list(list(size = 13), 
                                   list(size = 10)), 
                  ids = "inner") +
  geom_node_plot(gglist = list(
    geom_bar(aes(x = "", fill = PRI),
             position = position_fill(), color = "black"),
      theme_minimal(),
      scale_fill_manual(values = c("gray50", "gray80"), guide = FALSE),
      scale_y_continuous(breaks = c(0, 1)),
    xlab(""), 
    ylab("Probability"),
    geom_text(aes(x = "", group = PRI,
                  label = stat(count)),
              stat = "count", position = position_fill(), vjust = 1.1)),
    shared_axis_labels = TRUE)
  return(g)
}

pri.stump.SLEP <- rpart(PRI ~ SLEP, data = binned.train, method = "class", control = rpart.control(xval = nrow(binned.train)))
pri.stump.PAIN <- rpart(PRI ~ PAIN, data = binned.train, method = "class", control = rpart.control(xval = nrow(binned.train)))
pri.stump.IMAT <- rpart(PRI ~ IMAT, data = binned.train, method = "class", control = rpart.control(xval = nrow(binned.train)))
pri.stump.AGEN <- rpart(PRI ~ AGEN, data = binned.train, method = "class", control = rpart.control(xval = nrow(binned.train)))
pri.stump.YRIN <- rpart(PRI ~ YRIN, data = binned.train, method = "class", control = rpart.control(xval = nrow(binned.train)))
pri.stump.ASIA <- rpart(PRI ~ ASIA, data = binned.train, method = "class", control = rpart.control(xval = nrow(binned.train)))

# most interesting are IMAT, YRIN, ASIA
p.stump.slep <- tree_plot(pri.stump.SLEP, "SLEP Stump") + theme(panel.background = element_rect(fill = "white"))
p.stump.pain <- tree_plot(pri.stump.PAIN, "PAIN Stump") + theme(panel.background = element_rect(fill = "white"))
p.stump.imat <- tree_plot(pri.stump.IMAT, "IMAT Stump") + theme(panel.background = element_rect(fill = "white"))
p.stump.agen <- tree_plot(pri.stump.AGEN, "AGEN Stump") + theme(panel.background = element_rect(fill = "white"))
p.stump.yrin <- tree_plot(pri.stump.YRIN, "YRIN Stump") + theme(panel.background = element_rect(fill = "white"))
p.stump.asia <- tree_plot(pri.stump.ASIA, "ASIA Stump") + theme(panel.background = element_rect(fill = "white"))


```


```{r random_forest}



```



